The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:

GEM Established Entrepreneurship Rate

GEM Nascent Entrepreneurship Rate

GEM Entrepreneurial Intention

GEM Perceived Capabilities

GEM Fear of Failure

GEM Perceived Opportunities

GDP Annual Growth Rate

.

>>>>

In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages before importing one dataset per variable mentioned above:

GEM Established Entrepreneurship Rate  
GEM Nascent Entrepreneurship Rate  
GEM Entrepreneurial Intention  
GEM Perceived Capabilities  
GEM Fear of Failure   
GEM Perceived Opportunities  
GDP Annual Growth Rate

We cleaned our data by getting rid of unnecessary characters like the "X" to which we substituted ""nothing. We called the new versions with different names.

One issue we then faced was to merge our datasets all together into a two-dimension table whilst we had three dimensions to take into account: country, year and variable. Therefore, for each dataset, we moved the years from columns to rows, without getting rid of the country labels of course. Thus the first column would be the list of countries, the second the list of years (same for each country: 2001 ... 2013), the third the variable of interest.

We merged the datasets two by two until we we obtained the final dataset that would allow us to test the data and have an attempt at one or two regressions.
